\LevelZero{Language}\label{ch:language}

\LevelOne{Definition}
The files inside \tbf{config/fuji/languages/} directory are called \tbf{language files}. \\
Each \tbf{language file} defines a table to map a \tbf{language key} into a \tbf{language value}.

\LevelOne{Modify the default language used by fuji}
You can modify the \tbf{default language} in \mainconfig file.
After that, issue \cmd{/fuji reload} command to apply the changes.

\LevelOne{Control how the text is sent}
The \tbf{language value} only defines what is the text.
It didn't define how to use that text.
You can use \tbf{language instructions} to specify how to use that \tbf{language value}. \\
Currently supported language instructions:
\begin{description}
    \item [1. Send the text via action bar] {If the language value starts with \str{[send-action-bar]}}
    \item [2. Send the text via main title] {If the language value starts with \str{[send-main-title]}}
    \item [3. Send the text via sub title] {If the language value starts with \str{[send-sub-title]}}
    \item [4. Suppress the sending of this text] {If the language value starts with \str{[suppress-sending]}}
\end{description}
If no \tbf{language instruction} is used, we will send the \tbf{text} via the \tbf{message}.

\LevelOne{Control the text sending stream}
For each fuji command, you can use \str{--silent true/false} and \str{--stdout true/false} to control the text sending stream during the command execution.\\
For example:\\
1. The \cmd{/fly others Steve --silent true} will \tbf{cancel the text sending} during the execution of \cmd{/fly} command.\\
2. The \cmd{/fly others Steve --stdout true} will \tbf{log the text sending into the console} during the execution of \cmd{/fly} command.\\
3. You can use the \str{--silent true} and \str{--stdout true} both at the same time. \\
4. You can pass the flags into sub-command: \cmd{/run as console --stdout true send-message @r Hello}


\LevelOne{Enable multiple language support}
You can enable the \str{language} module, to provide the multiple language support for each player, and respect their client side language option.

\begin{tips}{How to know what languages are loaded and in use?}
    Issue \cmd{/fuji inspect languages} command, to see what language files are loaded.
\end{tips}
